%{\small \textcolor{myblue}{This is a generic version of the real AMCOS conference booklet for which this \LaTeX{} template was generated. All information about the use and distribution of this template, and all related codes, can be found at \url{https://github.com/maximelucas/AMCOS\_booklet}.}}
%
\section{WiN: Women in Networks Workshop}
The COSTNET Women in Networks Workshop will bring together senior and junior (mainly) women international scientists working in the field of Networks modelling and Networks applications. Activities will be spread over three days.

During the first two days, there will be afternoon interactive breakout discussion sessions in which participants will form small groups to independently discuss important topics in the field.

In particular, the first session will be devoted to highlight the main challenges and open questions in the modelling and validation of Networks.

The second interactive session will address the identification of potential solutions to the problems discussed.

The objectives of the interactive afternoon sessions will be:
\begin{itemize}
\item identifying main challenges;
\item propose possible problems solutions;
\item deciding priorities, strategy, and vision;
\item improving/establishing scientific collaborations and networking;
\item gathering ideas for research grant proposals;
\item ascertaining user requirements for bioinformatics tools;
\item generating ideas for designing web/software interfaces.
\end{itemize}
The 3rd, and last day, afternoon session will be dedicated to the discussion of poster presentations. Participants' posters will be displayed over the workshop around the lunch break area.

\section{COSTNET: the European Cooperation for Statistics of Network Data Science.}


The WiN workshop is a targeted COSTNET event. COSTNET is COST Action CA15109 (\url{https://costnet.webhosting.rug.nl/}) which aims to foster an international European collaboration on the emerging field of statistics of network data science. COSTNET facilitates interaction and collaboration between diverse groups of statistical network modellers, establishing a large and vibrant interconnected and inclusive community of network scientists. \\
\textbf{Chair:}
Professor Ernst Wit,
University of Groningen,
Netherlands. \\	
\textbf{Vice Chair:}
Professor Gesine Reinert,
University of Oxford,
Department of Statistics,
United Kingdom.



\section{Organizing committee}
\begin{center}
\begin{tabular}{ll}
Luisa Cutillo & School of Mathematics,University of Leeds\\
Jeanine Houwing-Duistermaat & School of Mathematics, University of Leeds


\end{tabular}
\end{center}
\section{Logistic}
Special thanks for the conference arrangements to:
\begin{center}
\begin{tabular}{ll}
Helen Copeland & Secretarial Assistant, School of Mathematics, University of Leeds\\
Iris Burger & Secretarial Office, Department of Statistics, University of Munich\\ 

\end{tabular}
\end{center}

